%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Classicthesis-Styled CV
% LaTeX Template
% Version 1.0 (22/2/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{scrartcl}

\usepackage[utf8]{inputenc} % Para poder meter caracteres guays como ≤≥
\usepackage{parcolumns}

\newcommand{\accentColor}{NavyBlue}
\reversemarginpar % Move the margin to the left of the page

\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}} % New command defining the margin text style

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[nochapters]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage[LabelsAligned]{currvita} % Use the currvita style for the layout of the document
\usepackage[left=3cm, right=2.5cm, top=2cm, bottom=1cm]{geometry}

\renewcommand{\cvheadingfont}{\LARGE\color{\accentColor}} % Font color of your name at the top

\usepackage{hyperref} % Required for adding links	and customizing them
\hypersetup{colorlinks, breaklinks, urlcolor=\accentColor, linkcolor=\accentColor} % Set link colors

\newlength{\datebox}\settowidth{\datebox}{Spring 2011} % Set the width of the date box in each block
%\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{1.5em} #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\newcommand{\NewEntry}[3]{%
\begin{parcolumns}[colwidths={1=1 em, 2=3 cm}, distance=1em]{3}
\colchunk{}
\colchunk{\noindent \small \textit{#1}}
\colchunk{#2 \\ #3}
\end{parcolumns}%
\vspace{0.5em}} % Add some white space after each new entry

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize\vspace{1em}} % Define a command for descriptions of each entry - change spacing and font sizes here

\newcommand{\IndentDescription}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\hspace{1.5em}\footnotesize{#1}\par\normalsize\vspace{1em}}

\newcommand{\PersonalDataEntry}[2]{\NewEntry{#1}{#2}{} \vspace{-1.3em}}

\newcommand{\header}[1]{{\small \textit{#1} \\ \vspace{0.2em}}}
\newcommand{\jobcat}[1]{\hangindent=2.5em\hangafter=0\vspace{1em} \noindent\textsc{#1} \hspace{1em}}
%----------------------------------------------------------------------------------------

\begin{document}

\thispagestyle{empty} % Stop the page count at the bottom of the first page

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\begin{cv}{\spacedallcaps{Guillermo Juli\'an Moreno}}\vspace{1.5em} % Your name

\noindent\spacedlowsmallcaps{Personal Information}\vspace{0.5em} % Personal information heading

\PersonalDataEntry{email}{\href{mailto:gjulianm@outlook.com}{gjulianm@outlook.com}} % Email address
%\NewEntry{email}{\href{mailto:guillermo.julian@estudiante.uam.es}{guillermo.julian@estudiante.uam.es}} % Email address

\PersonalDataEntry{other links}{\href{http://github.com/gjulianm}{Github} |
\href{http://www.linkedin.com/pub/guillermojuli\%C3\%A1n-moreno/37/712/35b}{LinkedIn} |
\href{http://stackoverflow.com/users/783010/gjulianm}{Stack Overflow}}

%\input{PersonalInfo.tex}

\vspace{2em}
\noindent\spacedlowsmallcaps{Description}\vspace{1em}

\Description{I'm always willing to learn new things, open to new approaches and ideas. I have a deep interest in research, tackling problems that require more than just a little bit of thought and development and discovering new knowledge and possibilities. Programming-wise, I enjoy both low-level languages that leverage full control of the computer and allow me to tweak and get every last drop of performance, and high-level languages that allow me to abstract and devise complex architectures.}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------
\vspace{2em}
\noindent\spacedlowsmallcaps{Work Experience}\vspace{1em}

\NewEntry{March 2015 \\ Present}{Intern}{\textsc{Naudit HPCN}}

\Description{Naudit HPCN is the spin-off of the HPCN-UAM research group. I continued there with my work on parallel numeric algorithms and Linux capture driver development. Additionally, I analyzed and checked the health .}

\NewEntry{December 2013 \\ March 2015}{Intern}{\textsc{High Performance Computing and Networking - UAM}}

\Description{HPCN-UAM is a research group in the Universidad Autónoma de Madrid (UAM), where I familiarez myself with high performance networking and computing. I worked on network dependency analysis, Linux driver development for traffic capture, numeric algorithms optimizations with OpenCL and network protocol reverse engineering and analysis.}

\NewEntry{January 2012 \\ October 2015}{Freelance developer}

\Description{During my studies at university, I also worked as a freelancer in various projects:

\jobcat{Windows Phone development} Designed and developed from scratch \href{http://windowsphone.com/s?appid=2ca75e0f-69a4-42e9-b788-dedc31afb82a}{Ocell} (as a side project), \href{http://www.windowsphone.com/s?appid=3399a605-f046-471a-bf58-a13348f5d01b}{Clases de Apoyo} and Emergencias 066, an application for emergency assistance in Mexico. Assisted \href{http://www.softwhisper.es/}{Softwhisper} in the development of a Windows Phone application.

\jobcat{eGarante} Designed and created the \href{http://blog.egarante.com/2013/08/05/uso-de-la-herramienta-para-captura-de-evidencias-web/}{Firefox addon} for \href{http://egarante.com}{eGarante}. This addon allows users to digitally sign and timestamp any web page, including private ones (e.g. Twitter, Facebook). Developed a Python service to automatically sign user's conversations on social networks.

\jobcat{Other work} Specialized in C\# and networking in C/C++, I helped in the refactor and correction of existing projects and developed analyzers and dissectors for network traces, including parsers in restricted environments (e.g. OpenWRT routers).
}

\NewEntry{January 2010\\ October 2015}{Writer, \textsc{Weblogs SL}}

\Description{During five years, I wrote about insights, news and analysis about web, software and technology in Genbeta and Xataka, two of the most visited spanish publications in their category.

\href{http://www.genbeta.com/autor/gjulianm}{Author page at Genbeta}, \href{http://www.xataka.com/autor/gjulianm}{Xataka}}


\NewEntry{October 2012\\ November 2014}{Coordinator at Xataka Windows, \textsc{Weblogs SL}}

\Description{Since its very beginning, I've been writer and coordinator at Xataka Windows, the Microsoft specialized spin-off of Xataka. I was responsible for the management of the publication's editorial team and for its contents.

\href{http://www.xatakawindows.com/autor/guillermo-julian}{Author page at Xataka Windows}}

%------------------------------------------------

\vspace{1em}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Education}\vspace{2em}

\NewEntry{2011 - 2016 (Expected)}{Double degree in Mathematics and Computer Engineering}{\textsc{Universidad Autónoma de Madrid}}

\Description{Apart from the  classes in Mathematics, Computer Science and Computer Engineering, I took advanced courses on advanced real analysis, functional analysis, image processing, algorithm design and neurocomputing.}

%------------------------------------------------
\vspace{3em}
\NewEntry{2009 - 2011}{International Baccalaureate \\ LOE (spanish) Baccalaureate}{\textsc{Instituto Ramiro de Maeztu, Madrid}}


%------------------------------------------------

\spacedlowsmallcaps{Publications}\vspace{1em}

\Description{\textit{(In review)} G. Julián-Moreno et al., Fast parallel $\alpha$-stable distribution function evaluation and parameter estimation using OpenCL in GPGPU, Parallel Computing.}

\Description{\textit{(In progress)} G. Julián-Moreno, End-of-degree project: Monitorization, capture and intelligent storage of network traffic at 40Gbps.}

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Programming skills}\vspace{1em}

\Description{\header{Languages - Advanced knowledge} C\#, C, C++, Java, Python, \LaTeX, Awk.}

\Description{\header{Languages - Medium knowledge} Ruby, Haskell, Matlab, Mathematica, Bash, Common Lisp, Bash, Javascript, HTML, CSS.}

\Description{\header{Frameworks and enviroments I've developed for}
Angular.js,
Azure,
Firefox's Addon SDK,
Glassfish,
jQuery,
Linux kernel,
OpenCL,
OpenWRT,
Rails,
Sage (mathematical),
Windows Phone,
Windows. }

\Description{\header{Technologies and software used} Sublime Text, Vim, Zsh, Visual Studio, Git, Github, TFS, Eclipse, Linux, OS X, Windows, Windows Phone, Android.}

%------------------------------------------------

\vspace{1em} % Extra space between major sections

\spacedlowsmallcaps{Other Information}\vspace{1em}

\newlength{\langbox} % Create a new length for the length of languages to keep them equally spaced
\settowidth{\langbox}{English} % Length equals the length of "English" - if you have a longer language in your list put it here

\Description{\header{Languages} \parbox{\langbox}{\textsc{Spanish}}\ \ $\cdotp$\ \ \ Mothertongue}

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\parbox{\langbox}{\textsc{English}}\ \ $\cdotp$\ \ \ Advanced (conversationally fluent)}

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\parbox{\langbox}{\textsc{French}}\ \ $\cdotp$\ \ \ Basic (simple words and phrases only)}
\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\parbox{\langbox}{\textsc{Catalan}}\ \ $\cdotp$\ \ \ Basic (only spoken)}

\vspace{1em} % Negative vertical space to counteract the vertical space between every \Description command

%----------------------------------------------------------------------------------------

\end{cv}

\end{document}
